Dynamic Load Balancing for\\Heterogeneous Systems

### 2011-12-05 paper/paper.tex
Added Load-balacing schemes section.

>>>>

\section{Load Balancing Schemes}
A naive implementation of CPU+GPU co-processing will in many cases lead to an imbalance
of work for either the CPU or GPU.  To deal with this problem we will investigate the
use of 2 different load balancing schemes in addtion to the performance of a CPU-only or
a GPU-only solution.

The first load balancing scheme that was implemented was a static division of work between
the CPU and the GPU at a specified ratio.  This ratio was user-defined allowing for best 
performance after runtime benchmarking.  The main cause of overhead for this method of
load-balancing is that of a varying workload.  If the workload for the kernel is imbalanced
between workgroups, it is impossible to statically determine the proper amount of work
to put on each kernel.  Improper allocation of work to each device will not allow both
devices to be fully utilized, and application performance will not be optimal.

To address the issue of a dynamic work load between workgroups for kernels, we also used
a dynamic load-balancing scheme.  In this scheme the worksgroups were grouped into larger
chunks.  Each device is initially allocated one chunk of work to work on.  As each chunk
is retired by the device a new chunk is allocated.  This load-balancing scheme will still
not guarentee optimal performance.  Within a work chunk, a single long-running workgroup
can hold up the entire device, not allowing other kernels to execute on open SMs.
